\chapter{Chapter 1: How to Hold a Glass of Water with Your Hands}

Water is very important for our bodies, and it's good
to drink water every day. But do you know how to pick up a glass of water and
drink it like a pro? It's easy!
First, find a glass of water that you want to drink.
It can be big or small, but make sure it's not too heavy for you to hold. If
you're not sure, you can ask a grown-up to help you pick a good glass.
Next, get ready to pick up the glass of water. Stand
or sit in a comfortable position, and make sure the glass is within reach.
Now, it's time to use your hands to pick up the glass.
First, put one hand on the bottom of the glass. This will help you balance the
glass and keep it steady.
Then, use your other hand to hold the glass on the
side. Make sure you're not holding the top of the glass, because that's where
the water is!
Once you have both hands on the glass, slowly lift it
up and bring it to your mouth. Remember to keep the glass steady with your hand
on the bottom.
Now, take a small sip of water. You can close your
mouth around the rim of the glass and use your lips to sip the water. Don't
forget to swallow the water!
If you want more water, take another small sip. It's
better to take small sips of water than to drink a lot at once.
When you're done drinking, put the glass back down on
the table or counter. Remember to always use both hands to pick up and hold
your glass of water!
Drinking water is an important part of staying healthy
and feeling good. Now that you know how to pick up a glass of water like a pro,
you can drink water whenever you're thirsty. Great job!
But wait, what happens if you spill some water? Don't worry, it happens to everyone sometimes. Just use a towel or napkin to clean it up. And next time, try to hold the glass a little tighter or take smaller sips of water.
It's also important to remember that we should drink
water every day, even when we're not feeling thirsty. Our bodies need water to
stay hydrated and healthy.
When you're playing outside or doing activities, it's
a good idea to take breaks and drink some water. This will help you feel better
and have more fun!
And one more thing, always ask a grown-up if you need
help with drinking water or anything else. They're there to help you and keep
you safe.
Now that you know how to hold a glass of water like a
pro, you're ready to take on the world! Stay hydrated, stay healthy, and keep learning new things.
