\chapter{Chapter 2: Which Cup to Choose - Picking the Best Cup for Drinking Water
}

Did you know that there are many different kinds of
cups that you can use to drink water? Some cups are big, some are small, and
some are just right.
When you're choosing a cup to drink water, it's
important to pick one that is easy for you to hold and drink from. Here are
some things to keep in mind:
First, look for a cup that is not too heavy for you to
hold. It should be easy for you to pick up and drink from.
Next, make sure the cup is not too big or too small.
If the cup is too big, it might be hard for you to hold and drink from. If the
cup is too small, you might need to refill it often.
It's also important to choose a cup that is easy to
clean. Cups with smooth surfaces are easier to clean than cups with lots of
ridges or designs.
You can choose a cup that has your favorite color or
design on it, or you can choose a plain cup. What's important is that you can
drink water easily and comfortably from it.
And remember, it's always a good idea to wash your cup
with soap and water before and after you drink from it. This will help keep it
clean and ready for the next time you want to drink water.
Now that you know how to pick the best cup for
drinking water, you can stay hydrated and healthy like a pro!
 
If you're not sure which cup to choose, you can always ask a grown-up for help. They can help you find a cup that is just right for you.
And did you know that you don't always have to use a
cup to drink water? You can also use a reusable water bottle. A water bottle is
a container that you can fill up with water and carry with you wherever you go.
Water bottles come in many different colors and
designs, just like cups. Some even have fun characters or pictures on them! And
they're great for taking to school, the park, or anywhere else you might go.
When you're using a water bottle, make sure to use the
cap or straw to drink from. And always remember to close the cap or put the
straw back when you're done drinking. This will help prevent spills and keep
your water bottle clean.
So whether you're using a cup or a water bottle, make
sure to choose one that you like and that is easy for you to drink from. That way, you can stay
hydrated and feel great!
 
Now that you know how to choose the best cup or water bottle for drinking water, it's time to practice! You can start by picking out your favorite cup or water bottle and filling it up with water.
Try holding the cup or water bottle and taking small
sips of water. See how it feels in your hand and in your mouth. If you're using
a water bottle, practice opening and closing the cap or straw.
Remember to always drink water throughout the day,
especially when you're thirsty or doing activities. And don't forget to wash
your cup or water bottle regularly to keep it clean and ready for use.
Congratulations, you've now learned how to choose the
best cup or water bottle for drinking water like a pro! In the next chapter,
we'll learn more about how much water we should drink every day to stay healthy
and hydrated.
