\chapter{Chapter 3: How Much Water Should You Drink - Staying Hydrated for a Healthy Body
}
Did you know that our bodies are made up of mostly
water? That's why it's important to drink water every day to keep our bodies
healthy and hydrated.
So how much water should you drink every day? Well, it
depends on your age, size, and activity level.
As a general rule, 3-year-olds should drink about 4-5
cups of water every day. This might sound like a lot, but it's important to
drink water throughout the day to stay hydrated.
You can drink water with meals or snacks, or you can
drink water in between. And remember, it's always a good idea to drink water
when you're feeling thirsty.
If you're doing activities or playing outside, you
might need to drink even more water to stay hydrated. That's because your body
loses water when you sweat, and it needs to be replaced.
So how can you tell if you're drinking enough water?
One way is to check the color of your pee. If it's a light yellow or clear
color, that's a good sign that you're hydrated. If it's a dark yellow or brown
color, that means you need to drink more water.
And don't forget, you can also get water from foods
like fruits and vegetables. Watermelon, cucumbers, and grapes are examples of
foods that are high in water.
Now that you know how much water you should drink
every day, you can stay hydrated and healthy like a pro!
 
Remember to always drink water when you're thirsty, and don't wait until you feel really thirsty to drink. This is because when you feel thirsty, your body is already starting to get dehydrated.
And if you're not a big fan of drinking plain water,
you can try adding some flavor to it! You can add a slice of lemon, lime, or
cucumber to your water for a refreshing taste.
But remember, it's important to drink mostly plain
water to stay hydrated. Sugary drinks like soda and juice can be tasty, but
they can also make you feel more thirsty and dehydrated.
So always try to drink mostly water, and remember to
drink enough water every day to keep your body healthy and hydrated.
Congratulations, you've now learned how much water you
should drink every day to stay hydrated like a pro! In the next chapter, we'll
learn about the benefits of drinking water and how it can make you feel better.
